---
title: "Muziek Database"
author: "Connor Whalen"
date: "2024-07-12"
output:
  html_document:
    theme: readable
    highlight: textmate
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Welcome to the Muziek Spreadsheet
You are probably here because you want to listen to some more music. Maybe you are here because you want to see if your taste is better than your peers. NEWSFLASH: it isn't! So the real reason you are here then is to kneel at the feet of me and mine, send your condolences to you and yours, and open those ears up to what is right. Happy listening! 

#### Install packages. 
```{r packages.i, eval=FALSE, echo=FALSE}
install.packages("tidyverse")
install.packages("janitor")
install.packages("ggeffects")
install.packages("ggpubr")
install.packages("googlesheets4")
```

#### Load packages. 
```{r packages.l, echo=TRUE}
library(googlesheets4)
library(ggpubr)
library(ggeffects)
library(tidyverse)
library(readr)
library(dbplyr)
library(lubridate)
library(ggplot2)
```

## Instructions to load database
Load spreadsheet data using gs4 (pull directly fromt the sheet itself).
```{r gs4 load, include=FALSE, eval=FALSE}
gs4_auth(scopes = "spreadsheets.readonly") 
# muziekspreadsheet@gmail.com <-- sign in when prompted
# muziekspreadsheet3@Tm3H@cR <-- password for google account
muziek_main <- read_sheet("https://docs.google.com/spreadsheets/d/1QH27wRqhg-6MS9vdQt7C73dLpHvsv3nov9YgxcZOlJQ/edit?pli=1&gid=0#gid=0") %>% 
  janitor::clean_names() 
```
#### Convert dates to the proper format
```{r}
muziek_main <- muziek_main %>%
  mutate(listen_date_c = as.Date(listen_date_c, format="%d-%m-%Y"),
         continuous_scale = as.numeric(listen_date_c - min(listen_date_c, na.rm = TRUE)))

muziek_main <- muziek_main %>%
  mutate(listen_date_a = as.Date(listen_date_a, format="%d-%m-%Y"),
         continuous_scale = as.numeric(listen_date_a - min(listen_date_a, na.rm = TRUE)))
```

#### Mutate lists into charecter variables
```{r}
muziek_main <- muziek_main %>%
  mutate(title = as.character(title)) %>%
  mutate(artist = as.character(artist)) %>%
  mutate(artist_album_number = as.character(artist_album_number)) %>%
  mutate(a_fav_track = as.character(a_fav_track))
```

### Plots 
```{r}
c_rr <- ggplot(muziek_main,
       aes(x = runtime_min, y = rating)) + geom_point() + xlab("Runtime")  + 
  ylab("Rating")  + theme_bw() + geom_smooth(method = lm)

a_rr <-  ggplot(muziek_main,
       aes(x = runtime_min, y = a_rating)) + geom_point() + xlab("Runtime")  + 
  ylab("Rating")  + theme_bw() + geom_smooth(method = lm)

c_rg <- ggplot(muziek_main,
       aes(x = gender, y = rating)) + geom_boxplot() + xlab("Gender")  + 
  ylab("Rating")  + theme_bw() + geom_smooth(method = lm)

a_rg <-  ggplot(muziek_main,
       aes(x = gender, y = a_rating)) + geom_boxplot() + xlab("Gender")  + 
  ylab("Rating")  + theme_bw() + geom_smooth(method = lm)

ggarrange(c_rr, a_rr, c_rg, a_rg, common.legend = TRUE, legend = "bottom", labels = c("A", "B", "C", "D"))
#####################

c_rd <- ggplot(muziek_main,
       aes(x = listen_date_c, y = rating)) + geom_point() + xlab("Date Listened")  + 
  ylab("Rating")  + theme_bw() + geom_smooth(method = lm)

a_rd <- ggplot(muziek_main,
       aes(x = listen_date_a, y = rating)) + geom_point() + xlab("Date Listened")  + 
  ylab("Rating")  + theme_bw() + geom_smooth(method = lm)

ggarrange(c_rd, a_rd, common.legend = TRUE, legend = "bottom", labels = c("A", "B"))

```




